Commutative character sheaves and geometric types for supercuspidal representations

### 2017-05-02 Geometric types.tex
Adding new corollary on the kernel of the forgetful functor

\begin{corollary} 
If $G$ is a smooth group scheme and $(\cs{L},\mu) \in \CS(G)$, then
the restriction of $\cs{L}$ to $G\der$ is trivial if and only if $(\cs{L},\mu) \cong q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$, for some $(\cs{L}\ab,\mu\ab) \in \CS(G\ab)$. \todo{What is the ``kernel'' of the forgetful functor?  Ie, is there a natural parameterization of the possible choices of $\beta$?}
\end{corollary}

@@

>>>>

\begin{corollary} 
If $G$ is a smooth group scheme and $(\cs{L},\mu) \in \CS(G)$, then
the restriction of $\cs{L}$ to $G\der$ is trivial if and only if $(\cs{L},\mu) \cong q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$, for some $(\cs{L}\ab,\mu\ab) \in \CS(G\ab)$.
\end{corollary}

@@

We may interpret this corollary as measuring how far $q^*$ is from being essentially surjective.  The next result shows that it is also not full.
Let $C$ denote the cokernel of the natural map
\[
\Hom(\pi_0(\bar{G})_{\mathcal{W}}, \EEx) \to \Hom(\pi_0(\bar{G}\der)_{\mathcal{W}}, \EEx),
\]
where $\pi_0(\bar{G})_\mathcal{W}$ denotes the covariants of the action of Frobenius on
the component group of $G$

\begin{corollary}
If $G$ is a smooth group scheme and $(\cs{L},\mu)$ is a character sheaf on $G$ with trivial restriction to $G\der$,
then the set of isomorphism classes of objects in $\CS(G\ab)$ mapping to $(\cs{L},\mu)$ under $q^*$ is a principal homogeneous space
for $C$.
\end{corollary}
\begin{proof}
By Proposition~\ref{prop:CSGabab}, it suffices to find the set of isomorphism classes in $\CSab(G)$ mapping to
$(\cs{L},\mu)$ under the forgetful functor.  By the previous corollary this set is nonempty.
If $(\cs{L},\mu,\beta)$ and $(\cs{L},\mu,\beta')$ both map to $(\cs{L},\mu)$, then $\beta' \circ \beta^{-1}$ is an
automorphism of the constant sheaf on $G\der$.  Conversely, if $\varphi$ is an automorphism of $(\EE)_{G\der}$
and $(\cs{L},\mu,\beta) \in \CSab(G)$ then $(\cs{L},\mu,\varphi \circ \beta) \in \CSab(G)$.  By \cite{cunningham-roe:13a}*{Thm. 3.9},
the automorphism group is isomorphic to $\Hom(\pi_0(\bar{G}\der)_{\mathcal{W}}, \EEx)$.  Finally, we note that any
automorphism $\alpha$ of $(\cs{L},\mu) \in \CS(G)$ defines an isomorphism $(\cs{L},\mu,\beta \circ \alpha|_{G\der}) \to (\cs{L},\mu,\beta)$.
Applying \cite{cunningham-roe:13a}*{Thm. 3.9} again yields the desired result.
\end{proof}
